%
% Chapter 9
%

\chapter{Conclusion}
\epigraph{A physicist is an atom's way of knowing about atoms.}{\textit{George Wald}}
\vskip 0.6in
\label{conclusion}

This dissertation describes two searches for lepton flavor violating decays. Both searches were performed with data collected by the CMS detector in 2016, in proton-proton collisions at the LHC, at a center-of-mass energy of 13\,TeV. Neither search found evidence of such BSM decays, and stringent upper exclusion limits have been set.

The search for SM Higgs (h) decaying into a muon and an electronically decaying tau ($\hmue$) is now a published result in a peer-reviewed journal~\cite{HIG-17-001}. This search (in combination with $\hmuhad$) has set most stringent upper bounds till date on the branching fraction of h decaying to $\mu\tau$. The observed (median expected) upper limits on $\mathcal{B}(\hmu)$ is 0.25 (0.25)\,\% at 95\% CL. Upper limit on off-diagonal $\mu\tau$ Yukawa couplings, derived from the above constraint, is also set to be $\sqrt{|Y_{\Pgm\Pgt}|^{2}+|Y_{\Pgt\Pgm}|^{2}}<1.43\times 10^{-3}$ at 95\% CL. These limits constitute a significant improvement over all previous results.

The search for lepton flavor violating decays of a neutral heavy Higgs boson (H) into a muon and an electronically decaying tau ($\hmue$) is complete, and on its way to being a peer-reviewed publication. This search (in combination with $\Hmuhad$) has set upper limits on product of H cross-section and branching ratio to $\mu\tau$. These observed (median expected) limits on $\sigma(\textrm{gg}\rightarrow \PH)\times\mathcal{B}(\Hmu)$ range from 51.9 (57.4)\,pb to 1.6 (2.1)\,pb for H masses in the range between 200 and 900 GeV. This search is the first direct search to set limits on this decay.

As the LHC's excellent performance in delivering proton-proton collisions continues, and CMS collects more an more  data, there is room for above results to improve. The very next step would be to perform these searches with the entire dataset collected in the run II (2015-2018) period. This would amount to more than 3 times the data used in the above searches, and with more innovative techniques to select signal events and reduce background processes, the sensitivity of the searches can be increased. 






